Graph-Based Neural Reconstruction from Skeletonized 3D Networks

### 2017-11-28 papers/cvpr2018/2_method.tex
updated figures

\begin{figure*}[htbp]
	\begin{center}
	\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}
	\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}
	\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}
	\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}
	\end{center}
	\caption{Outline of our approach, from left to right: Result of the pixel-based segmentation and agglomeration algorithm; segments of several selected neurons from the initial segmentation; extracted skeletonized 3D network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
	\label{fig:overview}
\end{figure*}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{./figures/skeleton1.png}
	\includegraphics[width=0.92\linewidth]{./figures/skeleton2.png}
	\caption{Example skeletons (in black) extracted from segments (blue and green) using the TEASER algorithm. \hp{there is enough space to add another example in this figure}}
	\label{fig:skeletonization}
\end{figure}

@@

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with non-negative edge weights $w_e$. The nodes correspond to label segments from the segmentation with edges between segments considered for merging. Ideally, our graph has edges corresponding to all of the segments that were erroneously split. To compute this graph we generate a skeleton for every segment in the pixel-based segmentation (Fig.~\ref{fig:overview}). The skeletonized 3D network is a simplified representation of the overall branching structure of the neurons. From these skeletons we identify potential merge locations and produce the corresponding edges for the graph. To find actual merges we run a classification CNN to generate edge weights corresponding to merge probabilities. We then use a multicut algorithm to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation. We will now discuss the three major components to our framework (graph creation, edge weights assignment, and graph partitioning) in more detail.

@@

First, we extract a skeleton from each segment in the label volume using the TEASER algorithm~\cite{sato2000teasar,zhao2014automatic}. Fig.~\ref{fig:skeletonization} shows an example of two extracted skeletons (in black). These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. We prune the joints that are within $t_{jnt} = 50$ voxels of each other to reduce unnecessary branching. We refer to joints that have only one connected neighbor as \textit{endpoints}. Many of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}). We make use of this fact to find merge candidates with the following two-pass pruning algorithm.

@@

\subsection{Edge Weights Assignment}
We assign edge weights $w_e$ to each edge where the weight corresponds to the probability that two nodes belong to the same neuron.
Instead of using handcrafted features to compute the similarity between adjacent nodes, we train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
If the probability of the nodes belonging to the same neuron is $p_e$, the edge weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$, where $\beta$ is a tunable parameter that encourages over or undersegmentation.
%Our  edge weights  correspond to probabilities that two endpoints $e$ in $\mathbb{S}_c$ belong to the same neuron and should be merged. \hp{check}

@@

%Fig.~\ref{fig:architecture} provides an overview of our CNN architecture.
We use the CNN architecture by Chatfield et al.~\cite{chatfield2014return}. It consists of three layers of double convolutions followed by a max pooling step. The first max pooling layer is anisotropic with pooling only in the $x$ and $y$ dimensions. The output of this final pooling step is flattened into a 1D vector that is input into two fully connected layers. The final layer produces probabilities with a sigmoid activation function~\cite{funahashi1989approximate}. All of the other activation functions are LeakyReLU~\cite{maas2013rectifier}.

>>>>

\begin{figure*}[htbp]
	\begin{center}
	\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}
	\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}
	\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}
	\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}
	\end{center}
	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several selected neurons from the initial segmentation; extracted skeletonized 3D network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
	\label{fig:overview}
\end{figure*}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.82\linewidth]{./figures/skeleton1.png}
	\includegraphics[width=0.82\linewidth]{./figures/skeleton2.png}
	\includegraphics[width=0.82\linewidth]{./figures/skeleton3.png}
	\caption{Example skeletons (in black) extracted from segments using the TEASER algorithm.}
	\label{fig:skeletonization}
\end{figure}

@@

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. The nodes correspond to label segments from the segmentation with edges between segments considered for merging. Ideally, our graph has edges corresponding to all of the segments that were erroneously split. To compute this graph we generate a skeleton for every segment in the pixel-based segmentation (Fig.~\ref{fig:overview}). The skeletonized 3D network is a simplified representation of the overall branching structure of the neurons. From these skeletons we identify potential merge locations and produce the corresponding edges for the graph. To find actual merges we run a classification CNN to generate edge weights corresponding to merge probabilities. We then use a multicut algorithm to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation. We will now discuss the three major components to our framework (graph creation, edge weights assignment, and graph partitioning) in more detail.

@@

First, we extract a skeleton from each segment in the label volume using the TEASER algorithm~\cite{sato2000teasar,zhao2014automatic}. Fig.~\ref{fig:skeletonization} shows an example of three extracted skeletons (in black). These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. We prune the joints that are within $t_{jnt} = 50$ voxels of each other to reduce unnecessary branching. We refer to joints that have only one connected neighbor as \textit{endpoints}. Many of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}). We make use of this fact to find merge candidates with the following two-pass pruning algorithm.

@@

\subsection{Edge Weights Assignment}
We assign edge weights $w_e$ to each edge where the weight corresponds to the probability that two nodes belong to the same neuron.
Instead of using handcrafted features to compute the similarity between adjacent nodes, we train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
If the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$, where $\beta$ is a tunable parameter that encourages over- or under-segmentation.
%Our  edge weights  correspond to probabilities that two endpoints $e$ in $\mathbb{S}_c$ belong to the same neuron and should be merged. \hp{check}

@@

%Fig.~\ref{fig:architecture} provides an overview of our CNN architecture.
We use the CNN architecture by Chatfield et al.~\cite{chatfield2014return}. It consists of three layers of double convolutions followed by a max pooling step. The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions. The output of this final pooling step is flattened into a 1D vector that is input into two fully connected layers. The final layer produces probabilities with a sigmoid activation function~\cite{funahashi1989approximate}. All of the other activation functions are LeakyReLU~\cite{maas2013rectifier}.

### 2017-11-28 papers/cvpr2018/paper.tex
updated figures

%%%%%%%%% TITLE
\title{Graph-Based Neural Reconstruction \\ from Skeletonized 3D Networks}
% Neural Reconstruction Using Skeletonized 3D Networks
% Neural Reconstruction with Top-Down Enhancements from Skeletonized 3D Networks
% Graph-Based Neural Reconstruction from Morphological Skeletons
%Robust Agglomeration using 3D Skeletonization of Labeled for Connectomics}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible.
Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions.
However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways.
We first generate skeletons in 3D from the membrane labels of the pixel-based segmentation.
We then simplify this skeletonized 3D network into a 3D graph with nodes corresponding to labels from the segmentation and edges identifying potential locations of segmentation errors.
We use a CNN classifier trained on ground truth data to generate edge weights on the 3D graph corresponding to error probabilities.
We then apply a multicut algorithm to generate a partition on the graph that improves the final segmentation.
Because the 3D graph is small and encodes top-down information our method is efficient and globally improves the neural reconstruction.
We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of \FIX{$X\times$}.
%The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
\end{abstract}
%%%%%%%%	% BODY TEXT

>>>>

%%%%%%%%% TITLE
\title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks}
% Neural Reconstruction Using Skeletonized 3D Networks
% Neural Reconstruction with Top-Down Enhancements from Skeletonized 3D Networks
% Graph-Based Neural Reconstruction from Morphological Skeletons
%Robust Agglomeration using 3D Skeletonization of Labeled for Connectomics}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible.
Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions.
However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways.
We first generate skeletons in 3D from the neuron labels of the pixel-based segmentation.
We then simplify this skeletonized 3D network into a 3D graph with nodes corresponding to labels from the segmentation and edges identifying potential locations of segmentation errors.
We use a CNN classifier trained on ground truth data to generate edge weights on the 3D graph corresponding to error probabilities.
We then apply a multicut algorithm to generate a partition on the graph that improves the final segmentation.
Because the 3D graph is small and encodes top-down information our method is efficient and globally improves the neural reconstruction.
We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average split variation of information improvement of 19.3\%.
%The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
\end{abstract}
%%%%%%%%	% BODY TEXT

### 2017-11-28 papers/cvpr2018/supplemental/performance.tex

All performance experiments ran on an Intel Core i7-6800K CPU 3.40 GHz with a Titan X Pascal GPU. 
All code is written in Python and will be freely available upon the paper decision.
We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for cuda 8.0.

@@

The network trained for $34$ epochs with each epoch taking approximately $1200$ seconds to complete.
Table \ref{table:performance} shows the total running time for each dataset for graph creation, CNN inference, and multicut partitioning. 
In all instances the time for these three steps combined was less than 100 seconds.
Currently extracting the skeletons with the TEASER algorithm is the bottleneck.
The skeleton for each label takes around $20-30$ seconds to generate. 
However, the process is parallelizable as each segment can be processed independently.
Faster skeleton extraction is an important area for future research, particularly to consider algorithms in different fields~\cite{fazekas2008skeletonization}.
There is some existing research of fast topologically preserving skeleton generation and their applications to existing medical images (e.g. blood vessels, the colon)~\cite{palagyi2001sequential}.

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{c c c } \hline
		& \textbf{Kasthuri Vol. 1} & \textbf{Kasthuri Vol. 2} \\ \hline
		Graph Generation & 34.76s & 35.90s \\
		Inference & 38.47s & 37.13s \\
		Multicut & 22.94s & 22.90s \\ \hline
		Total Time & 96.17s & 95.93s \\ \hline
		& \textbf{FlyEM Vol. 1} & \textbf{FlyEM Vol. 2} \\ \hline
		Graph Generation & 46.52s & 48.97s \\
		Inference & 12.55s & 10.91s \\
		Multicut & 30.30s & 30.14s \\ \hline
		Total Time & 89.37s & 90.02s \\ \hline
	\end{tabular}
	\caption{Performance of each step of the framework for all four datasets.}
	\label{table:performance}
\end{table}

>>>>

All performance experiments ran on an Intel Core i7-6800K CPU 3.40 GHz with a Titan X Pascal GPU. 
All code is written in Python and will be freely available upon the paper decision.
We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for CUDA 8.0.

@@

We train the network for $34$ epochs with each epoch taking approximately $1200$ seconds to complete.
Table \ref{table:performance} shows the total running time for each dataset for graph creation, CNN inference, and multicut partitioning. 
In all instances the time for these three steps combined is less than 100 seconds.
Currently extracting the skeletons with the TEASER algorithm is the bottleneck.
The skeleton for each label takes around $20$ to $30$ seconds to generate. 
However, the process is parallelizable as each segment can be processed independently.
Faster skeleton extraction is an important area for future research.
There is some existing research on fast skeleton generation and its applications to existing medical images (e.g. blood vessels, the colon)~\cite{palagyi2001sequential}.

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{c c c } \hline
		& \textbf{Kasthuri Vol. 1} & \textbf{Kasthuri Vol. 2} \\ \hline
		Graph Creation & 34.76s & 35.90s \\
		Inference & 38.47s & 37.13s \\
		Multicut & 22.94s & 22.90s \\ \hline
		Total Time & 96.17s & 95.93s \\ \hline
		& \textbf{FlyEM Vol. 1} & \textbf{FlyEM Vol. 2} \\ \hline
		Graph Creation & 46.52s & 48.97s \\
		Inference & 12.55s & 10.91s \\
		Multicut & 30.30s & 30.14s \\ \hline
		Total Time & 89.37s & 90.02s \\ \hline
	\end{tabular}
	\caption{Performance of each step of the framework for all four datasets.}
	\label{table:performance}
\end{table}

### 2017-11-28 papers/cvpr2018/supplemental/skeletonization.tex

We remove all nodes from the graph corresponding to labels with fewer than $t_{seg}$ voxels (Section 3.1).
Figure \ref{fig:node-pruning} shows the results of varying $t_{seg}$ on two different quantities for the Kasthuri training volume. 
The blue line indicates the number of nodes remaining in the graph.
The rate of node reduction decreases for larger thresholds since there are fewer labels of larger size. 
The green line shows the percent of voxels with a label pruned from the graph.
Ideally this number is low since we want to remove small segments which do not contribute much to the overall volume.
These are locations which we cannot improve the variation of information scores.
This ``volume lost" grows at an increasing rate as the larger segments are removed. 
Based on these curves we set $t_{seg} = 20000$ voxels.
With this threshold, we prune over half of the labels that correspond to around $1.5\%$ of the total volume.

@@

There are two parameters in the two-pass edge pruning algorithm, $t_{low}$ and $t_{high}$ (Section 3.2). 
The resulting graph should have the highest possible percentage of split errors still present while keeping the number of total edges low. 
We perform a search over varying thresholds for $40\textrm{nm} \leq t_{low} \leq 300 \textrm{nm}$ and $300 \textrm{nm} \leq t_{high} \leq 800 \textrm{nm}$ on the Kasthuri training dataset to find the parameter with the highest retention of true splits that keeps the number of total edges less than $6 \times$ the number of split errors.

>>>>

We remove all nodes from the graph corresponding to labels with fewer than $t_{seg}$ voxels (Section 3.1).
Figure \ref{fig:node-pruning} shows the results of varying $t_{seg}$ on two different quantities for the Kasthuri training volume. 
The blue line indicates the number of nodes remaining in the graph.
The rate of node reduction decreases for larger thresholds since there are fewer labels of larger size. 
The green line shows the percent of voxels with a label pruned from the graph.
Ideally this number is low since we want to remove small segments which do not contribute much to the overall volume.
This ``volume lost" grows at an increasing rate as the larger segments are removed. 
Based on these curves we set $t_{seg} = 20,000$ voxels.
With this threshold, we prune over half of the labels and only lose $1.5\%$ of the total volume.

@@

There are two parameters in the two-pass edge pruning algorithm, $t_{low}$ and $t_{high}$ (Section 3.2). 
The resulting graph should have a high percentage of the original split errors still present while keeping the number of total edges low. 
We perform a search over several thresholds from $40\textrm{nm} \leq t_{low} \leq 300 \textrm{nm}$ and $300 \textrm{nm} \leq t_{high} \leq 800 \textrm{nm}$ on the Kasthuri training dataset to find the parameter with the highest retention of split errors while keeping the total number of edges less than $6 \times$ the number of split errors.
